### 2018-02-23 pubs/itp-2018/sections/proof-reconstruction/strip.tex
[ paper ] all proofs have been removed.

\begin{proof}
The proof is by induction on the cases defined by the outcome of the
$\fuh_{1}$ function.
\begin{itemize}
  \item If $n = 0$, by definition in~\eqref{eq:uh-structured}
        we conclude $Γ ⊢ φ$.
  \item For $n \geq 1$, we use induction on the structure of the first
        argument.
\vskip 2mm
\begin{itemize}
\item Case $φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)$.
\begin{equation*}
  (\mathcal{D}_1)
  \begin{bprooftree}
    \AxiomC{$Γ ⊢ \fuh_1~(φ₁ ⇒ (φ₂ ∧ φ₃))~(\suc~n)$}
    \RightLabel{by~(\ref{eq:uh-structured})}
    \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₂)~n ∧ \fuh_1~(φ₁ ⇒ φ₃)~n$}
    \RightLabel{∧-proj₁}
    \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₂)~n$}
    \RightLabel{by~ind.~hyp.}
    \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
  \end{bprooftree}
\end{equation*}

\begin{equation*}
  (\mathcal{D}_2)
  \begin{bprooftree}
    \AxiomC{$Γ ⊢ \fuh_1~(φ₁ ⇒ (φ₂ ∧ φ₃))~(\suc~n)$}
    \RightLabel{by~(\ref{eq:uh-structured})}
    \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₂)~n ∧ \fuh_1~(φ₁ ⇒ φ₃)~n$}
    \RightLabel{∧-proj₂}
    \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₃)~n$}
    \RightLabel{by~ind.~hyp.}
    \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
    \end{bprooftree}
\end{equation*}

Now, using \texttt{⇒∧⇒\textsf{-to-}⇒∧} theorem from~\cite{AgdaProp},
\begin{equation*}
  \texttt{⇒∧⇒\textsf{-to-}⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃),
\end{equation*}
\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$\mathcal{D}_1$}
  \AxiomC{$\mathcal{D}_2$}
  \RightLabel{∧-intro}
  \BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
  \RightLabel{\tt ⇒∧⇒\textsf{-to-}⇒∧}
  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)}
  \end{bprooftree}
\end{equation*}
\item Other cases are proved in a similar way.
\end{itemize}
\end{itemize}
\end{proof}

@@

\begin{proof}
The proof is by induction on the structure of the
formula~$φ$ by following the equations in~\eqref{eq:strip-fixed}.
We present a straightforward case with double negation, the case for
conjunctions, and last, the case for a negated disjunction.
We refer the reader to~\cite{AgdaMetis} for the complete proof in \Agda.

∙~Case $φ ≡ ¬ (φ₁ ∨ φ₂)$.
We prove $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
From the conjunction of $¬ φ₁$ and $¬ φ₂$ by applying De Morgan Law
and the result follows.

\begin{equation*}
(\mathcal{D})\hspace{3mm}
\begin{bprooftree}
\AxiomC{$Γ ⊢ \fstrip₁~(¬ (φ₁ ∨ φ₂))~(\suc~n)$}
\RightLabel{by~(\ref{eq:strip-fixed})}
\UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~((¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n)$}
\RightLabel{∧-proj₁}
\UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n)$}
\RightLabel{Lemma~\ref{lem:inv-uh-lem}}
\UnaryInfC{$Γ ⊢ \fstrip₁~(¬ φ₁)~n$}
\RightLabel{by~ind.~hyp.}
  \UnaryInfC{$Γ ⊢ ¬φ₁$}
\end{bprooftree}
\end{equation*}
\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$\mathcal{D}$}
  \UnaryInfC{$Γ ⊢ ¬ φ₁$}
  \AxiomC{$Γ ⊢ \fstrip₁~(¬ (φ₁ ∨ φ₂))~(\suc~n)$}
  \RightLabel{by~(\ref{eq:strip-fixed})}
  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~((¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n)$}
  \RightLabel{∧-proj₂}
  \UnaryInfC{$Γ ⊢ \fuh~((¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n)$}
  \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
  \UnaryInfC{$Γ ⊢ (¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n$}
  \RightLabel{⇒-elim}
  \BinaryInfC{$Γ ⊢ \fstrip₁~(¬ φ₂)~n$}
  \RightLabel{by~ind.~hyp.}
  \UnaryInfC{$Γ ⊢ ¬ φ₂$}
  \end{bprooftree}
\end{equation*}
∙~  Other cases are proved in a similar way, see Appendix~\ref{app:strip-proof-case}.

\end{proof} % the proof continue...

@@

\begin{mainth}
\label{thm:strip}
Let $\text{n} : \Nat$ be the complexity measure of the strip function defined in Appendix~\ref{app:strip-cm}~\eqref{eq:strip-cm}.
Let $s₂$ and $s₃$ be the subgoals of the goal $φ$, that is,
$$\fstrip₁~φ~n~≡~s₂∧~s₃.$$
If $Γ ⊢ s₂$ and $Γ ⊢ s₃$ then $Γ ⊢ φ$.
\end{mainth}

\begin{proof}
\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$ Γ ⊢ s_1 $}
  \AxiomC{$ Γ ⊢ s_2 $}
  \RightLabel{∧-intro}
  \BinaryInfC{$Γ ⊢ s_1\wedge s_2$}
  \AxiomC{$\fstrip₁~φ~n ≡ s_1\wedge s_2 $}
  \RightLabel{\fsubst}
  \BinaryInfC{$Γ ⊢ \fstrip₁~φ~n$}
  \RightLabel{Lemma~\ref{lem:lem-inv-strip}}
  \UnaryInfC{$Γ ⊢ φ$}
\end{bprooftree}
\end{equation*}
\end{proof}

% -------------------------------------------------------------------

>>>>

@@

@@

\begin{mainth}
\label{thm:strip}
Let $\text{n} : \Nat$ be the complexity measure of the strip function defined in Appendix~\ref{app:strip-cm}~\eqref{eq:strip-cm}.
Let $s₂$ and $s₃$ be the subgoals of the goal $φ$, that is,
$$\fstrip₁~φ~n~≡~s₂∧~s₃.$$
If $Γ ⊢ s₂$ and $Γ ⊢ s₃$ then $Γ ⊢ φ$.
\end{mainth}
% -------------------------------------------------------------------
